What can Issues on GitHub and Google Code tell us about Bug Hazards in Android and Java?

### 2015-02-14 android-stacks.tex
Rewrite of best practice IV (document all exceptions thrown).
to make it more succinct.

\emph{IV- All exceptions explicitly thrown by reusable code should be documented.}
(\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,bloch2008effective}).
The exceptions thrown by a method are an important part of its interface,
since knowledge of them is required to use a method properly. 
Checked exceptions are already
part of the  method signature, making the method caller aware of the checked
exceptions it may have to handle.

According to~\cite{bloch2008effective}, it is
also wise to document (either on the \emph{exception interface} or using the @throws tag in Javadoc) 
the \emph{explicitly thrown} runtime exceptions as carefully as checked exceptions. 
These \emph{explicitly thrown} exceptions exclude the ones implicitly 
thrown by the runtime environment due to programming
mistakes.

This practice is mostly needed when developing  working with library/framework 
code -- as the developers do not have access to the source code. 
Doing so, the clients of such a library/framework
will be aware of all the exceptions a method can throw and can design the code
to deal with them ~\cite{Robil00}. If the developer fails to follow this practice 
 it will be difficult or even impossible for the caller to 
make effective use of such a method~\cite{wirfs2006toward, bloch2008effective},
and protect the system against unforeseen exceptions thrown by the utility code. 
This can lead to uncaught exceptions - one of the main causes of 
systems crashes.

>>>>

\emph{IV- All exceptions explicitly thrown by reusable code should be documented.}
(\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,bloch2008effective}).
For checked exceptions, this is automatically the case.
Bloch~\cite{bloch2008effective} furthermore recommends to document explicitly thrown
run time exceptions, either using a throws declaration in the signature, or using
the @throws tag in the Javadoc.
Doing so, in particular for public APIs of libraries or frameworks,
makes clients aware of all exceptions possibly thrown,
enabling them to design the code to deal with them and use the API effectively~\cite{Robil00,wirfs2006toward}.
